---
title: "SVAR"
author: "Abhijith & Vidhi Sharma"
date: '2022-05-08'
output: html_document
---
Importing all libraries required to run this R Mark down file.

```{r setup, include=FALSE}
library(vars)
library(mFilter)
library(tseries)
library(TSstudio)
library(forecast)
library(tidyverse)
```
Import the data set from the data folder. 

```{r}
macro <- read.csv('Data/USData.csv')
head(macro)
```

Setting the starting date of the data file and frequency of 4; since it is a quarterly data set.

```{r}
unemp <- ts(macro$`unemp`, start = c(1955,1,1), frequency = 4)
inflation <- ts(macro$ï..inflation, start = c(1955,1,1), frequency = 4)
interest <- ts(macro$interest, start = c(1955,1,1), frequency = 4)
```

Now plotting the time series variables using ts_plot ; you can read more about this function in tseries using ?'ts_plot'. 
This uses mostly used for web application library plotly ( graphically pleasing).
```{r}
ts_plot(unemp, title = "Unemp", Xtitle = "Time", Ytitle = "Unemp rate")
ts_plot(inflation, title = "inflation", Xtitle = "Time", Ytitle = "Inflation Rate")
ts_plot(interest, title = "interest", Xtitle = "Time", Ytitle = "interest rate")
```

Now setting up the sign restricitons; for this we have created a n*n (3*3, for our model) square matrix and then we have selected the restriction conditions based on the idea that no direct relationship between interest rate and inflation. This assumption is based on Svensson article on theoritical equation for monetary policy and lags, you can find the research paper here:

Svensson, L. E. 0. (n.d.). Policy rules for inflation targeting - NBER. Retrieved May 8, 2022, from https://www.nber.org/system/files/chapters/c7417/c7417.pdf 

#in our model we have used amat with dimesion (3*3).For the amat, the elements marked by NA entries are marked at the relavant positions. 
NA in our case is interest rate and unemployement rate , unemployement rate and inflation rate 



```{r}
amat <- diag(3)
#amat[2,1] <- NA
amat[3,1] <- NA
amat[3,2] <- NA
amat
```
Following AIC and HQ and SC values are used to decide the lag length

```{r}
sv <- cbind(interest,inflation, unemp)
colnames(sv) <- cbind( "interestrate","InflationRate","Unemprate" )
lagselect <- VARselect(sv, lag.max = 6, type = "both")
lagselect$selection
lagselect$criteria
```

Now that we have constraints for a reduced form to use on a VAR, Constructed a VAR for our model variables.
The estimation results are below:

```{r}
Model1 <- VAR(sv, p = 5, season = NULL, exog = NULL, type = "const")
Model1
```

Using the VAR model , we implied our constraints to reduce the VAR equation with our structural assumption
and thus we can see covariance matrix ( We used to upper triangle as zero and tried to find for lower triangle); keytake away is interest rate and unemployment rate and unemployment rate and inflation rate are moving in the same direction ( Since this data is for 60 years; it satisfies the theory for long run)
```{r warning=FALSE}

SVARMod1 <- SVAR(Model1, Amat = amat, Bmat = NULL, hessian = TRUE, estmethod =
                   c("scoring", "direct"))
SVARMod1
```

An impulse response is an response of a dynamic system for an exogenous signal, We can see this convey the price puzzle; with monetary tightening shock , we can see that inflation first increases and then decreases after short period of time. 
```{r}
SVARirf <- irf(SVARMod1, impulse = "interestrate", response = "InflationRate",n.ahead=100)
SVARirf
plot(SVARirf)

```

Forecast Error Variance Decomposition tells us for exogenous shocks to variables , the decomposition of error variance in forecast of each variable in dynamic equation. Interest rate error in forecasting is effected by both inflation and unemployment rate ( which in theory is true; Monetary authorities do take an action when these variables will be out of the bound limits ( as they adversly effect population's consumption and investment decisions))

```{r}

SVARfevd <- fevd(SVARMod1, n.ahead = 10)
SVARfevd
plot(SVARfevd)
```

